Project One Reproducible Research 
=================================
**Load Libraries**
```{r, echo=TRUE}
library(knitr)
library(tidyverse)
```
**Load data and Remove NA values**    
```{r, echo=TRUE}
activity <- read.csv("activity.csv", header = TRUE, sep = ",")
activity_1 <- activity[complete.cases(activity), ]
summary(activity_1) 
str(activity_1)
```
**Find the Mean and median number of steps taken each day**  
```{r, echo=TRUE}
perday <- group_by(activity_1, date)
stepsperday <- summarise(perday, total = sum(steps))
stepsperday
```
**Histogram of the total number of steps taken each day**  
```{r, echo=TRUE}
stepsPerDay <- with(activity_1, tapply(steps, date, FUN=sum))
hist(stepsPerDay, 
     col="blue",
     main = "Total number of steps per day", 
     xlab = "Total number of steps")
summary(stepsperday)
```
**Time series plot of the average number of steps taken **  
```{r, echo=TRUE}
agg <- aggregate(steps~interval, activity_1, mean)
plot(agg$interval, agg$steps, type = "l", col = 1, xlab = "Interval", 
     ylab = "Average Steps", main = "Average Number of Steps Taken")
```
**The 5-minute interval that, on average, contains the maximum number of steps **  
```{r, echo=TRUE}
rownum <- which.max(agg$steps)
maxsteps <- agg[rownum, ]$interval
maxsteps
```
**Code to describe and show a strategy for imputing missing data**  
```{r, echo=TRUE}
missing <- sum(is.na(activity$steps))
missing
```
**Create new data set imputing NAs**  
```{r, echo=TRUE}
getmean <- function(x){
    agg[agg$interval==x, ]$steps
}
activity2 <- activity
for(i in 1:nrow(activity2)){
    if(is.na(activity2[i,]$steps)){
        activity2[i, ]$steps <- getmean(activity2[1, ]$interval)
    }
}
imputesteps <- aggregate(steps ~ date, activity2, sum)
imputesteps
```
**Histogram of the total number of steps taken each day after missing values are imputed**  
```{r, echo=TRUE}
hist(imputesteps$steps, 
     col="blue",
     main = "total number of steps per day (Imputed)", 
     xlab = "Steps per day")
```
**loop through Date(day) to name all the days**  
```{r, echo=TRUE}
day <- weekdays(as.Date(activity2$date))
days <- vector()
for (i in 1:nrow(activity2)) {
    if (day[i] == "Saturday") {
        days[i] <- "Weekend"
    } else if (day[i] == "Sunday") {
        days[i] <- "Weekend"
    } else {
        days[i] <- "Weekday"
    }
}
activity$days <- days
activity$days <- factor(activity$days)

stepsbyday <- aggregate(steps ~ interval + days, data = activity, mean)
names(stepsbyday) <- c("interval", "days", "steps")
```
**Panel plot of average number of steps by days**    
```{r, echo=TRUE}
library(lattice)  
xyplot(steps ~ interval | days, 
       stepsbyday, 
       type = "l", 
       layout = c(2, 1), 
       xlab = "Interval",
       ylab = "Avg Number of steps")

```


